Appendix: A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-04 appendix.Rmd
update the table precentage

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  add_row(Pronoun = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Pronoun, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Pronoun", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"), 
                    booktabs = TRUE, label = "pronoun", caption = "Summary of pronoun distribution of subjects recuritted in this study.")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(age_group) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Age group` = age_group) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "age-group", caption = "Summary of age distribution of subjects recuritted in this study.")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  add_row(`Education` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I` = paste0(`Period I`, " (", round(`Period I`/443*100, 1), "%)")) %>%
  mutate(`Period II` = paste0(`Period II`, " (", round(`Period II`/443*100, 1), "%)")) %>%
  mutate(`Period III` = paste0(`Period III`, " (", round(`Period III`/443*100, 1), "%)")) %>%
  mutate(Total = paste0(Total, " (", round(Total/443*100, 1), "%)")) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "education", caption = "Summary of education distribution of subjects recuritted in this study.")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(previous_experience) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Previous experience` = previous_experience) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "experience", caption = "Summary of previous experience distribution of subjects recuritted in this study.")
```

@@

vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type == "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(7) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  scale_alpha_discrete(range = c(0.7, 0)) +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("I", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_manual(labels = c("0.5", "[0.25, 0.75]", "[0.125, 0.875]", "[0.0625, 0.09375]"),
                    values = c("white", rev(RColorBrewer::brewer.pal(5, "Blues")))) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period") +
  theme(legend.key = element_rect(colour = "black"))
```

>>>>

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  add_row(Pronoun = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Pronoun, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Pronoun", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"), 
                    booktabs = TRUE, 
                    label = "pronoun", 
                    caption = "Summary of pronoun distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(age_group) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Age group` = age_group) %>%
  add_row(`Age group` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Age group`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Age group", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "age-group", 
                    caption = "Summary of age distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  add_row(Education = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(Education, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Education", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "education", 
                    caption = "Summary of education distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(previous_experience) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Previous experience` = previous_experience) %>%
  add_row(`Previous experience` = "",
          `Period I` = sum(.$`Period I`),
          `Period II` = sum(.$`Period II`),
          `Period III` = sum(.$`Period III`),
          Total = sum(.$Total)) %>%
  mutate(`Period I %` = round(`Period I`/443*100, 1)) %>%
  mutate(`Period II %` = round(`Period II`/443*100, 1)) %>%
  mutate(`Period III %` = round(`Period III`/443*100, 1)) %>%
  mutate(`Total %` = round(Total/443*100, 1)) %>%
  select(`Previous experience`, 
         `Period I`, `Period I %`, 
         `Period II`, `Period II %`,
         `Period III`, `Period III %`,
         Total, `Total %`) %>%
  kableExtra::kable(format = "latex", 
                    col.names = c("Previous experience", 
                                  "Period I", "%", 
                                  "Period II", "%",
                                  "Period III", "%",
                                  "Total", "%"),
                    booktabs = TRUE, 
                    label = "experience", 
                    caption = "Summary of previous experience distribution of subjects recuritted in this study.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ungroup() %>%
  filter(type == "non-linearity") %>%
  select(type, exp, prop_detect) %>%
  mutate(exp = as.character(exp)) %>%
  sample_from_null(7) %>%
  ggplot() +
  geom_lv(aes(x = exp, y = prop_detect, fill = after_stat(LV)), varwidth = TRUE, k = 4) +
  facet_wrap(~k, ncol = 5) +
  theme_light() +
  scale_x_discrete(labels = c("I", "III")) +
  labs(fill = "Quantiles") +
  scale_fill_manual(labels = c("0.5", "[0.25, 0.75]", "[0.125, 0.875]", "[0.0625, 0.09375]"),
                    values = c("white", rev(RColorBrewer::brewer.pal(5, "Blues")))) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period") +
  theme(legend.key = element_rect(colour = "black"))
```

### 2023-04-04 appendix.tex
update the table precentage

\caption{\label{tab:pronoun}Summary of pronoun distribution of subjects recuritted in this study.}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Pronoun & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
He & 77 & 17.4 & 79 & 17.8 & 61 & 13.8 & 217 & 49.0\\
She & 78 & 17.6 & 77 & 17.4 & 61 & 13.8 & 216 & 48.8\\
Other & 5 & 1.1 & 4 & 0.9 & 1 & 0.2 & 10 & 2.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:age-group}Summary of age distribution of subjects recuritted in this study.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Age group & Period I & Period II & Period III & Total\\
\midrule
18-24 & 83 & 86 & 51 & 220\\
25-39 & 69 & 63 & 63 & 195\\
40-54 & 6 & 8 & 6 & 20\\
55-64 & 2 & 3 & 3 & 8\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:education}Summary of education distribution of subjects recuritted in this study.}
\centering
\begin{tabular}[t]{lllll}
\toprule
Education & Period I & Period II & Period III & Total\\
\midrule
High School or below & 41 (9.3\%) & 53 (12\%) & 33 (7.4\%) & 127 (28.7\%)\\
Diploma and Bachelor Degree & 92 (20.8\%) & 79 (17.8\%) & 66 (14.9\%) & 237 (53.5\%)\\
Honours Degree & 6 (1.4\%) & 15 (3.4\%) & 6 (1.4\%) & 27 (6.1\%)\\
Masters Degree & 21 (4.7\%) & 13 (2.9\%) & 16 (3.6\%) & 50 (11.3\%)\\
Doctoral Degree & 0 (0\%) & 0 (0\%) & 2 (0.5\%) & 2 (0.5\%)\\
\addlinespace
 & 160 (36.1\%) & 160 (36.1\%) & 123 (27.8\%) & 443 (100\%)\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:experience}Summary of previous experience distribution of subjects recuritted in this study.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Previous experience & Period I & Period II & Period III & Total\\
\midrule
No & 96 & 88 & 67 & 251\\
Yes & 64 & 72 & 56 & 192\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:pronoun}Summary of pronoun distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Pronoun & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
He & 77 & 17.4 & 79 & 17.8 & 61 & 13.8 & 217 & 49.0\\
She & 78 & 17.6 & 77 & 17.4 & 61 & 13.8 & 216 & 48.8\\
Other & 5 & 1.1 & 4 & 0.9 & 1 & 0.2 & 10 & 2.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:age-group}Summary of age distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Age group & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
18-24 & 83 & 18.7 & 86 & 19.4 & 51 & 11.5 & 220 & 49.7\\
25-39 & 69 & 15.6 & 63 & 14.2 & 63 & 14.2 & 195 & 44.0\\
40-54 & 6 & 1.4 & 8 & 1.8 & 6 & 1.4 & 20 & 4.5\\
55-64 & 2 & 0.5 & 3 & 0.7 & 3 & 0.7 & 8 & 1.8\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:education}Summary of education distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Education & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
High School or below & 41 & 9.3 & 53 & 12.0 & 33 & 7.4 & 127 & 28.7\\
Diploma and Bachelor Degree & 92 & 20.8 & 79 & 17.8 & 66 & 14.9 & 237 & 53.5\\
Honours Degree & 6 & 1.4 & 15 & 3.4 & 6 & 1.4 & 27 & 6.1\\
Masters Degree & 21 & 4.7 & 13 & 2.9 & 16 & 3.6 & 50 & 11.3\\
Doctoral Degree & 0 & 0.0 & 0 & 0.0 & 2 & 0.5 & 2 & 0.5\\
\addlinespace
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:experience}Summary of previous experience distribution of subjects recuritted in this study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
Previous experience & Period I & \% & Period II & \% & Period III & \% & Total & \%\\
\midrule
No & 96 & 21.7 & 88 & 19.9 & 67 & 15.1 & 251 & 56.7\\
Yes & 64 & 14.4 & 72 & 16.3 & 56 & 12.6 & 192 & 43.3\\
 & 160 & 36.1 & 160 & 36.1 & 123 & 27.8 & 443 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}
